---
title: "BD wasting prevalence and trajectories"
author: "Andrew Mertens"
date: "January 18, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Exploring wasting prevalence and variability in Bangladesh
Using anthropometry measurements from EED subsample, combining their main study measurements and a their EED sub-study measurments (5 total measurements).

```{r, include=F}

#Useful functions:
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL, title="",hjust=0,vjust=-7) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))


    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
    #mtext("Title for Two Plots", outer = TRUE, cex = 1.5)
grid.text(title, gp = gpar(fontsize = 18), hjust=hjust,vjust=vjust)
  }









###Load in data
library(foreign)
library(dplyr)
library(washb)
library(tidyverse)


setwd("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Data/Untouched/")
load("washb-BD-EE-blind-tr.Rdata")
levels(treatment$tr)
treatment$tr <- factor(treatment$tr,levels=c("Control","WSH","Nutrition","Nutrition + WSH"))
levels(treatment$tr)

#Load in main study anthro
main_anthro<-read.csv("washb-bangladesh-anthro.csv",stringsAsFactors = TRUE)
head(main_anthro)
main_anthro<-main_anthro %>%
  rename(main_svy=svy) %>%
  select(dataid, childid, clusterid, main_svy, anthrodate, month, dob, aged, agem, agey, laz, laz_x, lazminus2, lazminus3, waz, waz_x, wazminus2, wazminus3, whz, whz_x, whzminus2, whzminus3,  bmiz, bmiz_x, hcz, hcz_x)

setwd("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Data/Cleaned/Andrew")
anthro<-read.csv("BD-EE-anthro.csv")


#Merge treatment information 
dim(anthro)
d<-left_join(anthro,treatment, by="clusterid")
dim(d)
head(d)
table(d$tr)


#Append main study anthro data to EE anthro data
    #First, drop main study children not in EE
EEchildren<-d %>% select(dataid, childNo, svy) %>% distinct(dataid, childNo)

dim(EEchildren)
dim(main_anthro)
anthrochildren<-semi_join(main_anthro, EEchildren, by = "dataid", "childNo") 
dim(anthrochildren)

#Clean EE and main study datasets into appendable forms
head(anthrochildren)

anthrochildren<- anthrochildren %>%
    mutate(childNo=as.integer(substr(childid,2,2)), svy=main_svy+0.5, EEdata=0) %>%
    rename(date=anthrodate) %>%
    select(dataid, childNo, clusterid, svy, date, dob, aged,agem,agey,laz,laz_x, lazminus2, lazminus3, waz, waz_x, wazminus2, wazminus3, whz, whz_x, whzminus2, whzminus3)

head(d)
d<- d %>% 
  mutate(EEdata=1) %>% 
  rename(dob=DOB) %>% 
  select(dataid, childNo, clusterid, svy, date, dob, aged,agem,agey,laz,laz_x, lazminus2, lazminus3, waz, waz_x, wazminus2, wazminus3, whz, whz_x, whzminus2, whzminus3)

#Next, append main  study data to EE data
d<-bind_rows(d, anthrochildren)

#create unique child identifier
d$childid<-d$dataid*10+d$childNo
d$childid<-factor(d$childid)
```

###Crosstab wasting percentages over each survey round






```{r, include=F}
library(dplyr)
#Order children by sample dates and create new measurement number variable
d<-d %>%
  arrange(childid, childNo, date) %>%
  group_by(childid, childNo) %>%
  mutate(meas_num=min_rank(date)) %>%
  ungroup
```

```{r, echo=F}
library(dplyr)
d %>% group_by(meas_num) %>% summarize(wast_perc=mean(whzminus2, na.rm=T), severe_wast_perc=mean(whzminus3,  na.rm=T))

```

WHZ<-2 has ~10% prevalence across measurements, while WHZ<-3 has ~1% prevalence.

```{r, include=F}
#Vizualize wasting:

#Make line graphs of kids who have switched from wasted to non-wasted or vice-versa at least twice.
d2<- d %>% arrange(childid, meas_num) %>% mutate(wast_lag1=lag(whzminus2), swast_lag1=lag(whzminus3)) 
d2$wast_lag1[d$meas_num==1]<-NA
d2$swast_lag1[d$meas_num==1]<-NA
d2$wastchange<-d2$whzminus2-d2$wast_lag1
d2$swastchange<-d2$whzminus3-d2$swast_lag1


wastchange<-d2 %>% group_by(childid) %>%  mutate(num_wastchange=sum(abs(wastchange), na.rm=T)) %>% subset(num_wastchange>0 & !is.na(wast_lag1)) %>% ungroup
wastchange_plot<-ggplot(data=wastchange, aes(x=agey, y=whz, group=childid, color=childid)) +
    geom_line() +
    stat_smooth(aes(group = 1)) + 
    theme(legend.position = "none",axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    coord_cartesian(xlim=c(0,3), ylim = c(-4,0))


swastchange<-d2 %>% group_by(childid) %>%  mutate(num_swastchange=sum(abs(swastchange), na.rm=T)) %>% subset(num_swastchange>0 & !is.na(swast_lag1)) %>% ungroup
swastchange_plot<-ggplot(data=swastchange, aes(x=agey, y=whz, group=childid, color=childid)) +
    geom_line() +
    stat_smooth(aes(group = 1)) + 
    theme(legend.position = "none",axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    coord_cartesian(xlim=c(0,3), ylim = c(-4,0))




#Compare to stunting
d3<- d %>% arrange(childid, meas_num) %>% mutate(stunt_lag1=lag(lazminus2), sstunt_lag1=lag(lazminus3)) 
d3$stunt_lag1[d$meas_num==1]<-NA
d3$sstunt_lag1[d$meas_num==1]<-NA
d3$stuntchange<-d3$lazminus2-d3$stunt_lag1
d3$sstuntchange<-d3$lazminus3-d3$sstunt_lag1

stuntchange<-d3 %>% group_by(childid) %>%  mutate(num_stuntchange=sum(abs(stuntchange), na.rm=T)) %>% subset(num_stuntchange>0 & !is.na(stunt_lag1)) %>% ungroup
stuntchange_plot<-ggplot(data=stuntchange, aes(x=agey, y=laz, group=childid, color=childid)) +
    geom_line() +
    stat_smooth(aes(group = 1)) + 
    theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    coord_cartesian(xlim=c(0,3), ylim = c(-4,0))

sstuntchange<-d3 %>% group_by(childid) %>%  mutate(num_sstuntchange=sum(abs(sstuntchange), na.rm=T)) %>% subset(num_sstuntchange>0 & !is.na(sstunt_lag1)) %>% ungroup
sstuntchange_plot<-ggplot(data=sstuntchange, aes(x=agey, y=laz, group=childid, color=childid)) +
    geom_line() +
    stat_smooth(aes(group = 1)) +
    theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    coord_cartesian(xlim=c(0,3), ylim = c(-4,0))
```


##Plot trajectories
Plot out individual child trajectories, and smoothed average, of kids who who were ever wasted (top left), ever severely wasted (top right), ever stunted (bottom left), or ever severly stunted (bottom right)
```{r, echo=F}
multiplot(wastchange_plot, stuntchange_plot, swastchange_plot, sstuntchange_plot, cols=2)
```





##Make table of, at each time, percentage of kids who become wasted, who recover from wasting, or who stay wasted
```{r, echo=F}
wast_change_summary<-d2 %>% group_by(meas_num) %>% subset(!is.na(whzminus2)) %>%
  summarize(n_wast=sum(whzminus2, na.rm=T),per_wast=mean(whzminus2,na.rm=T),n_become_wast=sum(wastchange>0, na.rm=T), per_become_wast=mean(wastchange>0, na.rm=T)/mean(whzminus2,na.rm=T),n_recover_from_wast=sum(wastchange<0, na.rm=T), per_recover_from_wast=mean(wastchange<0, na.rm=T)/mean(whzminus2,na.rm=T),n_stay_wast=sum(wastchange==0 & whzminus2==1, na.rm=T), per_stay_wast=mean(wast_lag1==1 & whzminus2==1, na.rm=T)/mean(whzminus2,na.rm=T))
print(wast_change_summary, width=Inf)
```

##Make table of, at each time, percentage of kids who become stunted, who recover from wasting, or who stay stunted
```{r, echo=F}
stunt_change_summary<-d3 %>% group_by(meas_num) %>% subset(!is.na(lazminus2)) %>%
  summarize(n_stunt=sum(lazminus2, na.rm=T),per_stunt=mean(lazminus2,na.rm=T),n_become_stunt=sum(stuntchange>0, na.rm=T), per_become_stunt=mean(stuntchange>0, na.rm=T)/mean(lazminus2,na.rm=T),n_recover_from_stunt=sum(stuntchange<0, na.rm=T), per_recover_from_stunt=mean(stuntchange<0, na.rm=T)/mean(lazminus2,na.rm=T),n_stay_stunt=sum(stuntchange==0 & lazminus2==1, na.rm=T), per_stay_stunt=mean(stunt_lag1==1 & lazminus2==1, na.rm=T)/mean(lazminus2,na.rm=T))

print(stunt_change_summary, width=Inf)

```

Just from eyeballing the percentage of wasted/stunted children who change disease status between rounds, wasting is more variable, as expected.





