---
title: "Tables and Figures"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=20, message=FALSE, warning =FALSE)
```

```{r, include=FALSE}
rm(list=ls())
library(tidyverse)
library(knitr)
library(here)
load("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Results/Andrew/FU2_results.RDATA")
load("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Results/Andrew/FU2_pooled_results.Rdata")

#Plot parameters
scaleFUN <- function(x) sprintf("%.2f", x)

#Plot themes
theme_set(theme_bw())

#hbgdki pallet
tableau10 <- c("#1F77B4","#FF7F0E","#2CA02C","#D62728",
  "#9467BD","#8C564B","#E377C2","#7F7F7F","#BCBD22","#17BECF")

  
```


# N's by treatment arm

```{r, echo=F}

colnames(summary_res) <- c("Treatment Arm","FUT2 Status", "Number of Children", "Number of Mothers")
summary_res<-summary_res[!is.na(summary_res$`FUT2 Status`),]
summary_res$`FUT2 Status` <- factor(summary_res$`FUT2 Status`, levels=c("Positive","Negative","Inconclusive"))
summary_res <- summary_res %>% arrange(`Treatment Arm`, `FUT2 Status`)
knitr::kable(summary_res)
```

# Tables of associations between FUT2 status and growth outcomes (FUT2 as a risk factor)


### Child FUT2 status - continous outcomes

```{r, echo=F}

  knitr::kable(pooled_childFU2_growthRF_cont)
  cat("\n\n\n")
  

```

### Child FUT2 status - binary outcomes

```{r, echo=F}

  knitr::kable(pooled_childFU2_growthRF_bin)
  cat("\n\n\n")
  

```

### Maternal FUT2 status - continous outcomes

```{r, echo=F}
  knitr::kable(pooled_motherFU2_growthRF_cont)
  cat("\n\n\n")

```

### Maternal FUT2 status - binary outcomes

```{r, echo=F}
  knitr::kable(pooled_motherFU2_growthRF_bin)
  cat("\n\n\n")

```





# Tables of associations between FUT2 status and EED outcomes (FUT2 as a risk factor)


### Child FUT2 status

```{r, echo=F}

  knitr::kable(pooled_childFU2_RF_adj)
  cat("\n\n\n")
  

```

### Maternal FUT2 status

```{r, echo=F}
  knitr::kable(pooled_motherFU2_RF_adj)
  cat("\n\n\n")

```








# Tables of associations between FUT2 status and growth outcomes (FUT2 as a risk factor) - Stratified by measurement round


### Child FUT2 status - continous outcomes

```{r, echo=F}

  knitr::kable(res_childFU2_growthRF_cont)
  cat("\n\n\n")
  

```

### Child FUT2 status - binary outcomes

```{r, echo=F}

  knitr::kable(res_childFU2_growthRF_bin)
  cat("\n\n\n")
  

```

### Maternal FUT2 status - continous outcomes

```{r, echo=F}
  knitr::kable(res_motherFU2_growthRF_cont)
  cat("\n\n\n")

```

### Maternal FUT2 status - binary outcomes

```{r, echo=F}
  knitr::kable(res_motherFU2_growthRF_bin)
  cat("\n\n\n")

```




# Tables of associations between FUT2 status and EED outcomes (FUT2 as a risk factor) - Stratified by measurement round


### Child FUT2 status

```{r, echo=F}

  knitr::kable(res_childFU2_RF_adj)
  cat("\n\n\n")
  

```

### Maternal FUT2 status

```{r, echo=F}
  knitr::kable(res_motherFU2_RF_adj)
  cat("\n\n\n")

```




# Tables of WASH Benefits intervention effects, stratified by FUT2 status (FUT2 as an effect modifier)


## Child FUT2 status

```{r, echo=F, results='asis'}
for(i in 1:length(res_childFU2_EM_unadj)){
  
  cat("### Outcome: ",names(res_childFU2_EM_unadj)[i],"\n\n")
  print(knitr::kable(res_childFU2_EM_unadj[[i]]))
  
  cat("\n\n\n")
  
}
```

## Maternal FUT2 status

```{r, echo=F, results='asis'}
for(i in 1:length(res_motherFU2_EM_unadj)){
  
  cat("### Outcome: ",names(res_motherFU2_EM_unadj)[i],"\n\n")
  print(knitr::kable(res_motherFU2_EM_unadj[[i]]))
  
  cat("\n\n\n")
  
}
```

 


